---
title: "PDF Presentations Using the Universität Innsbruck Corporate Design"
author: "Gabriele Mustermann"
subtitle: "An Implementation via Quarto and beamer"
url: "https://www.uibk.ac.at/statistics"
date: "2025-10-14"
format:
    beamer:
        slide_level: 2
        aspectratio: 169
        theme: uibk
        themeoptions: quarto,nototalframenumber,logo,foot,license
        header-includes:
          - \headerimage{6}
          - \footertext{{\LaTeX} beamer theme with Quarto}

pdf-engine: pdflatex

# social media
author-mastodon: GabrieleMustermann2025
author-mastodon-server: social.uibk.ac.at
author-bluesky: Mustermann25
author-website: https://www.uibk.ac.at/
author-email:   Gabriele.Mustermann@uibk.ac.at
---


## Overview

**Demo:** Instead of authoring beamer slides in the Universität Innsbruck corporate design
in LaTeX it is also possible to use Markdown/Quarto.

\smallskip

**Installation:** You either need to have the `uibk` beamer theme files/images in your
local folder or install them in your TEXMF tree. See the documentation for the beamer
theme for more details

::: {.callout-tip}
# Quarto

[Quarto](https://quarto.org/) is an open-source scientific and technical publishing system.
It allows to create a wide variety of output documents (web pages, presentations, books, etc.)
from Markdown text files, also containing code in Python, R, Julia, or Observable.
:::


## Introduction

**Itemized lists:**

* Level 1
    * Level 2
        * Level 3

. . .

**Incremental enumerated list:**

::: {.incremental}
1. First item
2. Second item
3. Third item
:::



## Spacing

Three classes are available for vertical spacers, namely
`\smallskip`, `\medskip` and `\bigskip` which can be used via LaTeX:

```
\medskip
```

In this sentence we have ...

... the default paragraph skip. In this sentence ...

\smallskip


... there is a `\smallskip`. In this sentence ...

\medskip

... there is a `\medskip`. And finally we have ...

\bigskip

... a `\bigskip`.



## Formatting

**Text highlighting:**

~~strike~~, **bold**, _italic_, [UIBK blue]{.uibkblue}, [UIBK orange]{.uibkorange}

\medskip

**Predefined colors:**

- \fcolorbox{black}{uibkblue}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad blue (`uibkblue`)
- \fcolorbox{black}{uibkbluel}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad light blue (`uibkbluel`)
- \fcolorbox{black}{uibkorange}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad orange (`uibkorange`)
- \fcolorbox{black}{uibkorangel}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad light orange (`uibkorangel`)
- \fcolorbox{black}{uibkgray}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad gray (`uibkgray`)
- \fcolorbox{black}{uibkgraym}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad medium gray (`uibkgraym`)
- \fcolorbox{black}{uibkgrayl}{\rule{0pt}{.6em}\rule{.5em}{0pt}} \quad light gray (`uibkgrayl`)


## Beamer blocks

### Block

This block uses `uibkblue` and `uibkbluel`. It starts with:

`### Block`


### Alert block {.alert}

This block uses `uibkorange` and `uibkorangel`. It starts with:

`### Alert block {.alert}`



### Example block {.example}

This block uses `uibkgraym` and `uibkgrayl`. It starts with:

`### Example block {.example}`



## Quarto callout blocks

::: {.callout-note}
# Note

Note that there are five types of callouts, see below.
:::

::: {.callout-warning}
# Warning

Callouts provide a simple way to attract attention.
:::

::: {.callout-important}
# Callout is important

Danger, callouts will really improve your writing.
:::


## Callout blocks

::: {.callout-tip}
# Callout with caption

This is an example of a callout with a caption.
:::

:::{.callout-caution collapse="true"}
## Callout caution

Callout with caution.
:::


## Code execution

Quarto allows to create dynamic content in several programming languages:

- [R][ref-R]
- [Python][ref-python]
- [Julia][ref-julia]
- [Observable][ref-observable]

::: {.medskip}
:::

::: {.callout-note}
# Executing Python code
If a `.qmd` contains both R and Python chunks, the R package [`reticulate`](https://rstudio.github.io/reticulate/)
is required which moderates between R and Python.

If only Pyton is used, `jupyter` is used to execute/render Python chunks.
:::


## Code execution

**Some R code:**

```{r r-histogram}
#| echo: true
#| fig: true
#| fig-width: 8
#| fig-height: 3
#| fig-cap: Histogram of random variable `x`.
x <- rnorm(300, 3, 1)
hist(x)
```


## Linear regression model

**Data:**

```{r r-data}
#| echo: true
data("airquality")
head(airquality, n = 8)
```

## Linear regression model

**Estimating the model:**

```{r r-linear-model-estimation}
#| echo: true
m <- lm(Ozone ~ Temp, data = airquality)
```

**Model summary:**

\tiny
```{r r-linear-model-coef}
summary(m)
```

## Linear regression model

**Visualization:**

```{r r-linear-model-summary}
#| echo: !expr '-1'
#| fig-height: 3.9
#| fig-width: 5.5
#| out-width: 47%
par(mar = c(4, 3, 1, 1))
plot(Ozone ~ Temp, data = airquality)
abline(m, col = "tomato", lwd = 3)
```


## Code execution

**Some Python code:**

```{python py-numpy}
#| echo: true
import numpy as np
x = np.random.normal(size = 100)
m = float(x.mean())
print(f"The average of the random variable `x` is: {m:.3f}")
```


## Histogram plot

```{python py-matplotlib}
#| echo: true
#| out-width: 50%
from matplotlib import pyplot as plt
tmp = plt.hist(x, color = "#cecece")
plt.title("histogram") 
plt.show()
```



## Column layout

:::: {.columns}

::: {.column width="40%"}
First column, 35% width.

More text continues here, if necessary across several lines within the same column.
:::

::: {.column width="60%"}
Second column, 65% width.

Even more text here.
:::

::::


## Getting up

- Turn off alarm
- Get out of bed

## Going to sleep

- Get in bed
- Count sheep


---

## Thank you for your attention!
\bigskip \bigskip

|             |                                                                                      |
|:------------|:-------------------------------------------------------------------------------------|
| _Mastodon:_ | [@{{< meta author-mastodon >}}@{{< meta author-mastodon-server >}}](https://{{< meta author-mastodon-server >}}/@{{< meta author-mastodon >}}) |
| _Bluesky:_  | [@{{< meta author-bluesky >}}](https://bsky.app/profile/{{< meta author-bluesky >}}) |
| _Website:_  | [{{< meta author-website >}}]({{< meta author-website >}})                           |
| _Email:_    | [{{< meta author-email >}}](mailto:{{< meta author-email >}})                        |


[ref-R]: https://www.R-project.org/
[ref-python]: https://www.python.org/
[ref-julia]: https://julialang.org/
[ref-observable]: https://observablehq.com/
[ref-fontawesome-ext]: https://github.com/quarto-ext/fontawesome
