---
title: "HTML Presentations Using the Universität Innsbruck Corporate Design"
author: "Gabriele Mustermann (<a href='mailto:gabriele.mustermann@uibk.ac.at'>Gabriele.Mustermann@uibk.ac.at</a>)"
subtitle: "An Implementation via Quarto and reveal.js"
institute: "<a href=\"https://www.uibk.ac.at/statistics\" target=\"_blank\"><code>https://www.uibk.ac.at/statistics</code></a>"
format:
    uibk-revealjs:
        self-contained: true
        date: 2025-10-14
        footer: Quarto/reveal.js presentation theme
        auto-stretch: false

## To overwrite author-* details uncomment the lines below and
## adjust the value on the right hand side of the colon.
# author-mastodon:     GabrieleMustermann2025
# author-mastodon-url: https://social.uibk.ac.at
# author-bluesky:      Mustermann25
# author-website:      https://www.uibk.ac.at/statistik
# author-email:        Gabriele.Mustermann@uibk.ac.at

# Options:
#  slide-number: true      # default
#  slide-number: false     # do not show slide numbers
#  slide-number: "c"       # compact; show slide number only (not total slide number)
slide-number: "c"

# Options:
#  show-footer: true       # Show footer (default)
#  show-footer: false      # Do not show footer line
show-footer: true

# Option to disable the logo in the footer; re-define 'logo' as empty
#  logo: ""

# Options for including CC-BY licence logo
cc-by: true
---



## Overview

**Demo:** Creating HTML presentation slides in the Universität Innsbruck corporate design.
The following slides demonstrate some of the features/styling.

::: {.callout-tip}
# Quarto

[Quarto](https://quarto.org/) is an open-source scientific and technical publishing system.
It allows to create a wide variety of output documents (web pages, presentations, books, etc.)
from Markdown text files, also containing code in Python, R, Julia, or Observable.
:::


::: {.bigskip}
:::


**Infrastructure:** Custom Quarto extension `uibk-revealjs`.
 
::: {.callout-caution}
# Under construction
The extension `uibk-revealjs` is an early release and may be updated/extended
in the future.
:::


::: {.bigskip}
:::


**Link:** [Quarto/reveal.js demo](https://quarto.org/docs/presentations/revealjs/demo/#/title-slide) in the official Quarto documentation.



## Installation/usage

**Installation:**

- The `uibk-revealjs` extension is provided along with this presentation template.
- It needs to be installed locally along with the Quarto [fontawesome-ext][ref-fontawesome-ext] extension.
- Tip: Adding the option `--no-prompt` in the code below suppresses the `[Y/n]` prompt.

```
quarto install extension .
quarto install extension quarto-ext/fontawesome
```

::: {.medskip}
:::


**Usage:** 

- The Quarto/Markdown source file is `slides-revealjs.qmd`.
- Rendering yields the HTML slides `slides-revealjs.html`.

```
quarto render slides-revealjs.qmd
```



## Known issues

* `E` (tools: PDF export mode) is not working.  
  Use `slides-beamer.qmd` instead for rendering directly to PDF.
* The banner on the `.closing` slides does not yet span the entire slide width.


## Introduction

### Heading 3 (`###`)

#### Heading 4 (`####`)

##### Heading 5 (`#####`)


::: {.medskip}
:::

### Itemized lists:

* Level 1
    * Level 2
        * Level 3


### Incremental enumerated lists:

::: {.incremental}
1. First item
2. Second item
3. Third item
:::



## Spacing

Three classes are available for vertical spacers, namely
`.smallskip`, `.medskip` and `.bigskip` which can be used with fenced divs like:

```
::: {.smallskip}
:::
```

In this sentence we have ...


... the default paragraph skip. In this sentence ...

::: {.smallskip}
:::


... there is a `.smallskip`. In this sentence ...

::: {.medskip}
:::

... there is a `.medskip`. And finally we have ...

::: {.bigskip}
:::

... a `.bigskip`.



## Formatting

### Text highlighting

~~strike~~, **bold**, _italic_, [UIBK blue]{.uibkblue}, [UIBK orange]{.uibkorange}

### Predefined colors

* []{.square .uibkblue} blue (`.uibkblue`)
* []{.square .uibkbluel} light blue (`.uibkbluel`)
* []{.square .uibkorange} orange (`.uibkorange`)
* []{.square .uibkorangel} light orange (`.uibkorangel`)
* []{.square .uibkgray} gray (`.uibkgray`)
* []{.square .uibkgraym} medium gray (`.uibkgraym`)
* []{.square .uibkgrayl} light gray (`.uibkgrayl`)



## Callout blocks

::: {.callout-note}
# Note

Note that there are five types of callouts, including: `note`, `tip`, `warning`, `caution`, and `important`.
:::

::: {.callout-warning}
# Warning

Callouts provide a simple way to attract attention, for example, to this warning.
:::

::: {.callout-important}
# Callout is important

Danger, callouts will really improve your writing.
:::

::: {.callout-tip}
# Callout with caption

This is an example of a callout with a caption.
:::

:::{.callout-caution collapse="true"}
## Callout caution

Callout with caution.
:::


## Code execution

Quarto allows to create dynamic content in several programming languages:

- [R][ref-R]
- [Python][ref-python]
- [Julia][ref-julia]
- [Observable][ref-observable]

::: {.medskip}
:::

::: {.callout-note}
# Executing Python code
If a `.qmd` contains both R and Python chunks, the R package [`reticulate`](https://rstudio.github.io/reticulate/)
is required which moderates between R and Python.

If only Pyton is used, `jupyter` is used to execute/render Python chunks.
:::


## Code execution

Some R code:

```{r r-histogram}
#| echo: true
#| fig: true
#| fig-height: 4.0
#| fig-width: 6.5
#| out-width: 60%
x <- rnorm(300, 3, 1)
hist(x)
```


## Tabsets with R code

::: {.panel-tabset}

### Linear model

```{r r-linear-model}
#| echo: true
data("airquality")
m <- lm(Ozone ~ Temp, data = airquality)
summary(m)
```

### Data

```{r r-data}
#| echo: true
head(airquality, n = 10)
```

### Visualization

```{r r-scatterplot}
#| echo: !expr '-1'
#| fig: true
#| fig-height: 3.9
#| fig-width: 5.5
#| out-width: 44%
par(mar = c(4, 3, 1, 1))
plot(Ozone ~ Temp, data = airquality)
abline(m, col = "tomato", lwd = 3)
```

:::



## Tabsets with Python code

::: {.panel-tabset}

### numpy

```{python py-numpy}
#| echo: true
import numpy as np
x = np.random.normal(size = 100)
float(x.mean().round(5))
```

### matplotlib

```{python py-matplotlib}
#| echo: true
#| out-width: 57%
from matplotlib import pyplot as plt
tmp = plt.hist(x, color = "#cecece")
plt.title("histogram") 
plt.show()
```

:::


## Column layout

:::: {.columns}

::: {.column width="40%"}
First column, 35% width.

More text continues here, if necessary across several lines within the same column.
:::

::: {.column width="60%"}
Second column, 65% width.

Even more text here.
:::

::::



# A New Chapter

## Getting up

- Turn off alarm
- Get out of bed

## Going to sleep

- Get in bed
- Count sheep


---

::: {.closing}
#### Thank you for your attention!

|                                             |                                                                                      |
|:--------------------------------------------|:-------------------------------------------------------------------------------------|
| {{< fa brands mastodon title="Mastodon">}}  | [@{{< meta author-mastodon >}}@{{< meta author-mastodon-server >}}](https://{{< meta author-mastodon-server >}}/@{{< meta author-mastodon >}}) |
| {{< fa brands bluesky title="Bluesky">}}    | [@{{< meta author-bluesky >}}](https://bsky.app/profile/{{< meta author-bluesky >}}) |
| {{< fa solid globe title="Website">}}       | [{{< meta author-website >}}]({{< meta author-website >}})                           |
| {{< fa solid at title="E-Mail">}}           | [{{< meta author-email >}}](mailto:{{< meta author-email >}})                        |
:::




[ref-R]: https://www.R-project.org/
[ref-python]: https://www.python.org/
[ref-julia]: https://julialang.org/
[ref-observable]: https://observablehq.com/
[ref-fontawesome-ext]: https://github.com/quarto-ext/fontawesome
